Turbulence in compact to giant HII regions

### 2022-02-18 strucfunc_paper.tex
Expand caption for the model strucfunc figure

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
 \caption{
   A model structure function for homogeneous fluctuations.
   (a)~Idealized structure function (blue line) and effects
   of observational limitations at small and large scales.
   (b)~Examples of inhomogeneous effects at large scales,
   which are not included in the model structure function.
 }
 \label{fig:model-strucfunc}
\end{figure*}

@@

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma^2\);
 \item Large scales: \(B(r) \to 2 \sigma^2\) for \(r \gg r_0\).
\end{enumerate}
In a previous paper, we used a different functional form
\citetext{See Fig.~13 of \citealp{arthur2016turbulence}}:
\(C(r) = 1/[1+(r/r_{0})^{m}]\), as proposed in \citet{1984ApJ...277..556S},
which behaves identically to equation~\eqref{eq:new-correlation-form}
in the first two regimes, but is more gradual in its approach
to the large-scale asymptote of \(2 \sigma^2\).
However, we find that equation~\eqref{eq:new-correlation-form}
provides a much improved fit to the observed structure functions
of our sample regions (see following section).

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
 \caption{
   Example of the model structure function for homogeneous fluctuations,
   together with a realization of the corresponding velocity field
   on a \(512 \times 512\) pixel grid.  
   (a)~Idealized structure function (blue line)
   for the parameters \(m = 1\) and \(r_0 = \SI{64}{pixels}\).
   Red and green lines show the effects of observational limitations
   at small scales (seeing and noise)
   and at large scales (finite-map effects).
   (b)~Examples of inhomogeneous effects at large scales,
   which are not included in the model structure function.
 }
 \label{fig:model-strucfunc}
\end{figure*}

@@

In order to capture these two behaviors,
We therefore propose the following idealized 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.
We use equation \eqref{eq:functional} to determine the structure function
from this model autocorrelation function.
The resultant model structure function has the following properties:
\begin{enumerate}[1.]
 \item Small scales: \(B(r) \propto r^m\) for \(r \ll r_0\);
 \item Correlation scale: \(B(r_0) = \sigma\pos^2\);
 \item Large scales: \(B(r) \to 2 \sigma\pos^2\) for \(r \gg r_0\).
 \end{enumerate}
An example is shown by the blue line in Figure~\ref{fig:model-strucfunc}a.

In a previous paper, we used a different functional form
\citetext{See Fig.~13 of \citealp{arthur2016turbulence}}:
\(C(r) = 1/[1+(r/r_{0})^{m}]\), as proposed in \citet{1984ApJ...277..556S},
which behaves identically to equation~\eqref{eq:new-correlation-form}
in the first two regimes, but is more gradual in its approach
to the large-scale asymptote of \(2 \sigma\pos^2\).
However, we find that equation~\eqref{eq:new-correlation-form}
provides a much improved fit to the observed structure functions
of our sample regions (see following section).
